Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-05 android-stacks.tex
intro 2

\noindent\emph{Internal Validity.} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases. Moreover, in this study we manually classified the exceptions 
related to programming mistakes. To ensure the quality of the analysis, 
we calculated the interrater agreement after three independent 
coders classified a randomly selected sample (of 25 exception 
types from the total 100); the interater agreement was high (96\%).

Another threat relates to the fact that parts of our analysis 
are based on the availability of stack traces on issues on Github and Googlecode. 
In using these datasets, we make an underlying assumption: the stack traces reported on issues are 
representative of valid crash information of the applications. 
One way to mitigate such threat would be to access to the full 
set of crash data per application. Although some services exist 
to collect crash data from mobile applications ~\cite{BugSe14,BugSn14,Googl14,Acra14},
they do not provide open access to the crash reports of their client applications.
In our study, we mitigated this threat by manually inspecting
the source code associated to a subset of the reported exception stack traces.
Such subset comprise the stack traces related to the main findings 
of the study (e.g., `ùndocumented runtime and checked exceptions",
and cross-type wrappings").

\noindent\emph{External Validity.} We limited out analysis to a subset of
existing open-source Android apps. We are aware that the reported exceptions 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats to validity are similar to the ones imposed on the other empirical studies 
which also used free or open-source Android apps ~\cite{Linar13,McDon13,ahimed}.
Moreover,  several exception stack traces that support the findings of this study
refered to exceptions comming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the ``fragilities" observed in this study are due to
characteristics of Java exception model, which can impose challenges 
the robustness of not ony to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Detecting Faults on Java Exception-Related Code.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source-code of 32 open-source systems, both for Java and .NET. They
observed that the action handlers were very simple (e.g., logging and present a
message to the user). Reimer and Srinivasan~\cite{reimer2003analyzing} listed a
set of bad practices on exception handling that hinder software maintainability
and robustness, based on their own experience with Java enterprise applications.
Our work differs from those

>>>>

\noindent\emph{Internal Validity.} We used a heuristics-based parser to mine
exceptions from issues.  Our parsing strategy was conservative by default; for
example, we only considered exception names using a fully qualified class name
as valid exception identifiers, while, in many cases, developers use the
exception name in issue description. Conservative parsing may minimize false
positives, which was our initial target, but also tends to increase false
negatives, which means that some cases may have not been identified as
exceptions or stack traces. Our limited manual inspection did not reveal such
cases. Moreover, in this study we manually classified the exceptions 
related to programming mistakes. To ensure the quality of the analysis, 
we calculated the interrater agreement after three independent 
coders classified a randomly selected sample (of 25 exception 
types from the total 100); the interater agreement was high (96\%). 
Another threat relates to the fact that parts of our analysis 
are based on the availability of stack traces on issues on Github and Googlecode. 
In using these datasets, we make an underlying assumption: the stack traces reported on issues are 
representative of valid crash information of the applications. 
One way to mitigate such threat would be to access to the full 
set of crash data per application. Although some services exist 
to collect crash data from mobile applications ~\cite{BugSe14,BugSn14,Googl14,Acra14},
they do not provide open access to the crash reports of their client applications.
In our study, we mitigated this threat by manually inspecting
the source code associated to a subset of the reported exception stack traces.
Such subset comprise the stack traces related to the main findings 
of the study (e.g., `ùndocumented runtime and checked exceptions",
and cross-type wrappings").

\noindent\emph{External Validity.} Our work use GHTorrent dataset. Although 
comprehensive and extensive is not an exact replica of Github. 
However, the results of this study does not depent on the analysis of
a complete Github dataset. Instead, we limited out analysis to a subset of
existing open-source Android projects availabe on GitHub and Googlecode.
Moreover, we are aware that the reported exceptions 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats to validity are similar to the ones imposed on the other empirical studies 
which also used free or open-source Android apps ~\cite{Linar13,McDon13,ahimed}.
Moreover,  several exception stack traces that support the findings of this study
refered to exceptions comming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the ``fragilities" observed in this study are due to
characteristics of Java exception model, which can impose challenges 
the robustness of not ony to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Detecting Faults on Java Exception-Related Code.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source-code of 32 open-source systems, both for Java and .NET. They
observed that the actions inside handlers were very simple (e.g., logging and present a
message to the user). Reimer and Srinivasan~\cite{reimer2003analyzing} listed a
set of bad practices on exception handling that hinder software maintainability
and robustness, based on their experience with Java enterprise applications.
Our work differs from those
